\begin{abstract}
% V1
% Recent work in real-time crowd-powered products has demonstrated the possibility of using human ``crowd workers'' to power live, low latency products that accomplish AI complete tasks. Human-only solutions remain expensive, and do not scale into production. We propose a \textit{active classification} approach to dramatically reduce the scaling cost of such systems, backed by a pool of unreliable crowd-workers. In order to achieve this, we investigate \textit{asynchronous active classification}, where multiple requests can be simultaneously ``in-flight.'' This paper analyzes the \textit{asynchronous requests problem} of how to behave optimally in the presence of asynchronous oracle queries that have not yet returned, and the \textit{optimal stopping problem} of when a classification is ``good enough'' in such a setting. Our solutions to these problems enable a system that shows dramatic improvement over the human-only, machine-only, and baseline human-machine hybrid alternatives in the cost-delay-accuracy tradeoff surface.
Recent work in crowd-powered products has demonstrated the potential of using ``crowd workers'' to power live, low latency systems that accomplish AI complete tasks. 
These systems suffer from high scaling cost, and the unreliability of workers.
We propose an \textit{active classification} approach to dramatically reduce the scaling cost and improve the accuracy of such systems.
In order to also achieve low latency, we investigate \textit{asynchronous} active classification, where multiple requests can be simultaneously ``in-flight.''
This leads to the twin challenges of how to behave optimally in the presence of asynchronous noisy oracle queries that have not yet returned, and when to return a classification that is ``good enough'' in such a setting.
We first reduce the problem of optimal asynchronous active classification to a Partial Monitoring game, by making use of Bayesian decision theory.
We show a bound on achievable regret in this setting, and demonstrate practical heuristics that approach this bound.
We also show adaptations for traditional Active Learning algorithms to our setting.
We show empirical demonstration of our proposed algorithms, which demonstrate dramatic improvement over the human-only, machine-only, and baseline human-machine hybrid alternatives in the cost-delay-accuracy tradeoff surface.
\end{abstract}

